\pkg{systemfit}: A Package for Estimating Systems of Simultaneous Equations in \proglang{R}

### 2008-09-12 pkg/inst/doc/systemfit.Rnw
removed some "\SweaveOpts{prefix.string=trash/<*>}" to avoid having a "trash" folder
git-svn-id: svn://svn.r-forge.r-project.org/svnroot/systemfit@964 591db2bd-e0a0-4d22-8c19-2192dbb7da31

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section[Using systemfit]{Using \pkg{systemfit}}\label{sec:Usage}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\SweaveOpts{prefix.string=trash/usage}
<<echo=FALSE>>=
options( prompt = "R> " )
@

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Replication of textbook results}\label{sec:reliability}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\SweaveOpts{prefix.string=trash/replication}
<<echo=FALSE>>=
options( prompt = "R> " )
@

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Computation times}\label{sec:timings}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\SweaveOpts{prefix.string=trash/timings}
<<echo=FALSE>>=
options( prompt = "R> " )
@

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section[Estimating systems of equations with sem]
   {Estimating systems of equations with \code{sem}}
\label{sec:sem}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\SweaveOpts{prefix.string=trash/sem}
<<echo=FALSE>>=
options( prompt = "R> " )
options( width = 75 )
@

>>>>

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section[Using systemfit]{Using \pkg{systemfit}}\label{sec:Usage}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
<<echo=FALSE>>=
options( prompt = "R> " )
@

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Replication of textbook results}\label{sec:reliability}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
<<echo=FALSE>>=
options( prompt = "R> " )
@

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Computation times}\label{sec:timings}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
<<echo=FALSE>>=
options( prompt = "R> " )
@

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section[Estimating systems of equations with sem]
   {Estimating systems of equations with \code{sem}}
\label{sec:sem}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
<<echo=FALSE>>=
options( prompt = "R> " )
options( width = 75 )
@
